\chapter{Evaluation Plan} \label{chapter:evaluation-plan}

\section{Software Validation}

To evaluate the technical aspects of the software created, the following areas will need to be tested during implementation phase:

\begin{itemize}
  \item \textbf{Database stress testing:} one of the more technical aspects to test is the database. I will need to stress test the database to prevent any performance issues when providing data for the user. I will also test whether the user's login details are stored securely in the database.
  \item \textbf{Unit testing:} unit testing will be conducted on the iOS application to make sure there are no errors in areas such as storing data to the phone's internal database and displaying map data on screen.
\end{itemize}

\section{Additional Evaluation}

As well as the software validation, qualitative aspects of the project also need to be evaluated. This part of the evaluation should not only be done at the end of project to reflect back on what I have achieved, but also during the implementation phase. This is to ensure that problems with the application can be fixed and re-implemented as quickly as possible and hence maintain a fast feedback loop between me and the user.

\begin{itemize}
  \item \textbf{Design of application:} to test the design of the application, a design survey will be conducted during the design phase of the project asking users what they think of initial mockups of the application. Another survey will then be conducted near the end of the project to assess whether the design of the application I have made is appealing to the user, along with anything I need to change.
  \item \textbf{Ease of use of application:} the ease of use of the application will be evaluated through user testing. Family and friends can test the application and give me feedback on how easy the application is to use, as well as what features are implemented well. Once I have implemented more features into the application, I will be able to beta test the app with other users. At this stage I could also conduct hallway testing where I give the app to a stranger and they give me their initial feedback.
  \item \textbf{Reflect on objectives:} once the project is nearing completion, I will look back and assess if have accomplished my original objectives listed in Section \ref{section:objectives} and the requirements in Section \ref{section:requirements}, or explain why I have not.
\end{itemize}

\section{Evaluation Timeline}

Following on from the project timeline in Section \ref{section:project-timeline}, I have created a detailed timeline listing each of the testing and evaluation tasks that should be completed during the project. The timeline can be seen in Table \ref{table:evaluation-plan}.

\begin{table}[hbt]
  \centering
  \begin{tabular}{|l|| *{17}{c|}}
    \hline
    \multirow{2}{*}{\textbf{Activity}} & \multicolumn{3}{c|}{\textbf{February}} & \multicolumn{4}{c|}{\textbf{March}} & \multicolumn{4}{c|}{\textbf{April}} & \multicolumn{5}{c|}{\textbf{May}} & \\
    \cline{2-18}
    & 13 & 20 & 27 & 6 & 13 & 20 & 27 & 3 & 10 & 17 & 24 & 1 & 8 & 15 & 22 & 29 & 5\\
    \hline
    \hline
    Design survey & \multicolumn{2}{c|}{\cellcolor{OliveGreen}} &&& \multirow{7}{*}{\rotatebox[origin=c]{90}{\textls{REVISION}}} & \multirow{7}{*}{\rotatebox[origin=c]{90}{\textls{EXAMS}}} &&&&&&&&&&&\\
    \hhline{*{5}{-}~~*{11}{-}}
    Database testing &&\cellcolor{OliveGreen}&&&&&&&&&&&&&&&\\
    \hhline{*{5}{-}~~*{11}{-}}
    Login security &&\multicolumn{2}{c|}{\cellcolor{OliveGreen}}&&&&&&&&&&&&&&\\
    \hhline{*{5}{-}~~*{11}{-}}
    Unit testing &&&\multicolumn{2}{c|}{\cellcolor{OliveGreen}}&&&\multicolumn{10}{c|}{\cellcolor{OliveGreen}}&\\
    \hhline{*{5}{-}~~*{11}{-}}
    User testing &&&&&&&\multicolumn{10}{c|}{\cellcolor{OliveGreen}}&\\
    \hhline{*{5}{-}~~*{11}{-}}
    Hallway testing &&&&&&&&&\multicolumn{8}{c|}{\cellcolor{OliveGreen}}&\\
    \hhline{*{5}{-}~~*{11}{-}}
    Final survey &&&&&&&&&&&&&&&\multicolumn{3}{c|}{\cellcolor{OliveGreen}}\\
    \hline
  \end{tabular}
  \caption{Detailed evaluation timeline}
  \label{table:evaluation-plan}
\end{table}

A lot of the technical testing will be done throughout the implementation, including the database stress testing and the login security tasks. The surveys conducted at the start and end of the implementation section, along with the reflection on the initial objectives, will allow me to assess whether what I have made can be constituted as a success.


