\chapter{Project Plan}

\section{Requirements} \label{section:requirements}

Based on the broad objectives from Section \ref{section:objectives} and the background research conducted in Chapter \ref{chapter:background}, a detailed list of technical requirements was created. The objective that each requirement supports is shown in brackets.

% add paragraph here or after requirements as to why you chose to do each one

\begin{enumerate}[label=\textbf{Req \arabic*}]
    \item Build a fully functioning iOS application with a simple design and an easy-to-use user interface (\textbf{Obj 3}).
    \item Allow the user to track the routes of the walks they go on, as well as provide statistics about the walk such as distance travelled and calories burned (\textbf{Obj 1}).
    \item During a walk, the application should display certain points of interest on a map near the user's current location (\textbf{Obj 2}).
    \item Each user should be able to register an account within the application and publish their tracked walks to their profile if they wish (\textbf{Obj 1}).
    \item The application should display a list of the most popular walks in the area around you, with each walk containing statistics about how many times it has been walked and which user has walked it the most (\textbf{Obj 2}).
    \item Users should be able to invite other users to go on a walk together and schedule this walk for a point in the future (\textbf{Obj 1}).
    \item The application should contain some level of gamification - each user will have a score on their profile based on how far they have walked in total, how many walks they have been on and how often they go for a walk (\textbf{Obj 1}).
\end{enumerate}

\section{Project Timeline} \label{section:project-timeline}

% gantt chart made in excel
% overview one first, with design, implementation, exams, report writing and evaluation
% more detailed one just focusing on implementation (what needs to be done when)

With the requirements of the project established, a project timeline could be created showing how much time each task had been allocated. This timeline can be seen in Table \ref{table:project-plan}. At the time of writing this interim report, I have concluded my background research and just started designing the application for the project, with the implementation planned to start next week. I have labelled the week of \nth{20} March as exam week, with the thought that not much work will be done on the project due to revision.

\begin{table}[hbt]
  \setlength\tabcolsep{3 pt}
  \centering
  \begin{tabular}{|l|| *{24}{M{0.35cm}|}}
    \hline
    \multirow{2}{*}{\textbf{Activity}} & \multicolumn{4}{c|}{\textbf{January}} & \multicolumn{4}{c|}{\textbf{February}} & \multicolumn{4}{c|}{\textbf{March}} & \multicolumn{4}{c|}{\textbf{April}} & \multicolumn{5}{c|}{\textbf{May}} & \multicolumn{3}{c|}{\textbf{June}}\\
    \cline{2-25}
    & 9 & 16 & 23 & 30 & 6 & 13 & 20 & 27 & 6 & 13 & 20 & 27 & 3 & 10 & 17 & 24 & 1 & 8 & 15 & 22 & 29 & 5 & 12 & 19\\
    \hline
    \hline
    Research & \multicolumn{5}{c|}{\cellcolor{BrickRed}} & & & & & & \multirow{6}{*}{\rotatebox[origin=c]{90}{\textls{EXAMS}}} & & & & & & & & & & & & &\\
    \hhline{*{11}{-}~*{13}{-}}
    Design & & & & & \multicolumn{3}{c|}{\cellcolor{BurntOrange}} & & & & & & & & & & & & & & & & &\\
    \hhline{*{11}{-}~*{13}{-}}
    Implementation & & & & & & \multicolumn{5}{c|}{\cellcolor{YellowGreen}} & & \multicolumn{10}{|c|}{\cellcolor{YellowGreen}} & & &\\
    \hhline{*{11}{-}~*{13}{-}}
    Evaluation & & & & & & & & & & \cellcolor{OliveGreen} &  & \multicolumn{11}{c|}{\cellcolor{OliveGreen}} & &\\
    \hhline{*{11}{-}~*{13}{-}}
    Report & & & & & & & & & & & & & & & & & & & \multicolumn{5}{c!{\color{red}\vrule width 3pt}}{\cellcolor{ProcessBlue}} &\\
    \hhline{*{11}{-}~*{13}{-}}
    Presentation & & & & & & & & & & & & & & & & & & & & & & & \multicolumn{2}{c!{\color{red}\vrule width 3pt}}{\cellcolor{RoyalBlue}}\\
    \hline
  \end{tabular}
  \caption{Project timetable split into main tasks, with each column showing a week starting at the given date. The red line at the end of a coloured block represents the deadline for that row's task.}
  \label{table:project-plan}
\end{table}

In addition to the project timeline, I have constructed a more detailed version which shows when each subtask of the implementation needs to completed. By the end of the week of \nth{6} March I plan to have created a functioning skeleton application with some features implemented, so that evaluation can start as soon as possible.

The week of \nth{13} March has been labelled as revision week -- some project work might be done this week but I have allocated enough time in my timeline that this week can be solely for revision if needs be.

\begin{table}[hbt]
  \centering
  \begin{tabular}{|l|| *{16}{c|}}
    \hline
    \multirow{2}{*}{\textbf{Activity}} & \multicolumn{3}{c|}{\textbf{February}} & \multicolumn{4}{c|}{\textbf{March}} & \multicolumn{4}{c|}{\textbf{April}} & \multicolumn{5}{c|}{\textbf{May}}\\
    \cline{2-17}
    & 13 & 20 & 27 & 6 & 13 & 20 & 27 & 3 & 10 & 17 & 24 & 1 & 8 & 15 & 22 & 29\\
    \hline
    \hline
    Skeleton app & \cellcolor{YellowGreen} &&&& \multirow{10}{*}{\rotatebox[origin=c]{90}{\textls{REVISION}}} & \multirow{10}{*}{\rotatebox[origin=c]{90}{\textls{EXAMS}}} &&&&&&&&&&\\
    \hhline{*{5}{-}~~*{10}{-}}
    Set up web server &\multicolumn{2}{c|}{\cellcolor{YellowGreen}}&&&&&&&&&&&&&&\\
    \hhline{*{5}{-}~~*{10}{-}}
    Set up database &\multicolumn{2}{c|}{\cellcolor{YellowGreen}}&&&&&&&&&&&&&&\\
    \hhline{*{5}{-}~~*{10}{-}}
    Login system &&\multicolumn{2}{c|}{\cellcolor{YellowGreen}}&&&&&&&&&&&&&\\
    \hhline{*{5}{-}~~*{10}{-}}
    Track walks &&&\multicolumn{2}{c|}{\cellcolor{YellowGreen}}&&&&&&&&&&&&\\
    \hhline{*{5}{-}~~*{10}{-}}
    User Profile &&&&&&&\multicolumn{2}{c|}{\cellcolor{YellowGreen}}&&&&&&&&\\
    \hhline{*{5}{-}~~*{10}{-}}
    Popular walks &&&&&&&&\multicolumn{2}{c|}{\cellcolor{YellowGreen}}&&&&&&&\\
    \hhline{*{5}{-}~~*{10}{-}}
    Invite users for walk &&&&&&&&&&\multicolumn{3}{c|}{\cellcolor{YellowGreen}}&&&&\\
    \hhline{*{5}{-}~~*{10}{-}}
    Gamification &&&&&&&&&&&&&\multicolumn{2}{c|}{\cellcolor{YellowGreen}}&&\\
    \hhline{*{5}{-}~~*{10}{-}}
    Extensions &&&&&&&&&&&&&&&\multicolumn{2}{c|}{\cellcolor{YellowGreen}}\\
    \hline
  \end{tabular}
  \caption{Detailed implementation timeline}
  \label{table:implementation-plan}
\end{table}

\section{Extensions}

Should the requirements listed in Section \ref{section:requirements} be completed before the end of the project and there is enough time remaining, I have created a list of extensions that I would like to implement to extend the app's functionality.

\begin{enumerate}[label=\textbf{Ext \arabic*}]
  \item Add the ability for users to add each other as friends within the app.
  \item A recent activity feed could be added to show users what walks their friends have been on recently.
  \item The user should be able to take photos during a walk and then publish these photos to their profile along with the walk.
  \item Extend the gamification aspect of the app -- users could set each other challenges to encourage a higher level of fitness.
  \item Allow users to post a public invitation to a walk for any other user to join them.
  \item Implement a list of set walks nearby that the user could go on -- the London Loop for example.
\end{enumerate}